Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-26 SRO_Retest_Analyses.Rmd
cont working on retest exploration

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
sem <- function(x) {sd(x) / sqrt(length(x))}
options(digits = 4)
```

@@

# Different variable types

##

@@

Mean reliabilities for different kinds of variables (e.g. drift rates and NDs; separately for EZ and HDDM; subtraction vs basic variables - single vs. multiple)
```{r}
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(digits = 4)
```

@@

# Different task variable types

Mean reliabilities for different types of dependant variables

@@

We should probably take a closer look at model fits instead but this could be a first step.  
I'm not sure why there are so many more EZ variables than hddm variables.

```{r message=FALSE, warning=FALSE, fig.height=12, fig.width=9}
cor_df%>%
  select(-pearson) %>%
  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
  ggplot(aes(spearman, fill = clean_type))+
  geom_histogram(position='stack', alpha = 0.5)+
  theme_bw()+
  facet_wrap(var_type~var)+
  scale_fill_discrete(name = 'Clean type')

Average reliabilities

1. Cleaning doesn't seem to make a huge difference except for raw accuracies and hddm non_decision  
2. There are many more EZ variabiles but the few hddm variables have slightly higher reliabilities  
3. Raw accuracies seem to have the worst reliabilities on average while hddm parameters the highest

```{r}
cor_df%>%
  select(-pearson) %>%
  filter(grepl('EZ|hddm|_rt|_acc', dv)) %>%
  mutate(var_type = ifelse(grepl('EZ',dv), 'EZ', ifelse(grepl('hddm',dv), 'hddm', 'raw')),
         var = ifelse(grepl('_rt', dv), 'rt', ifelse(grepl('_acc', dv), 'acc', ifelse(grepl('_non_decision', dv), 'non_decision', ifelse(grepl('_thresh', dv), 'thresh', ifelse(grepl('_drift', dv), 'drift', NA)))))) %>%
  left_join(clean_cor_df[,c('spearman', 'dv')], by = 'dv') %>%
  gather(clean_type, spearman, -dv, -var_type, -var, -task) %>%
  mutate(clean_type = ifelse(clean_type == 'spearman.x','Before','After')) %>%
  group_by(var_type, clean_type, var) %>%
  summarise(mean_spearman = mean(spearman, na.rm=T),
            sem_spear = sem(spearman),
            num_vars = n())
```

## Model fits versus raw

```{r}
```

## Subtraction vs. Basic

```{r}
```

## Single vs. multiple

```{r}
```
